Weather and fuel as modulators of grassland fire behavior in the northern Great Plains

### 2022-01-31 paper/FigureGenerator_r1.Rmd
create structured abstract

```{r }
violin_cap <- f_nums(name = "violin_plots", 
                   caption = "Distribution of weather, fuel, and fire behavior data for fires in southwestern North Dakota (Hettinger, dark maroon) and central North Dakota (Central Grasslands, light blue). Horizontal gray lines denote 25%, 50% (median) and 75% quantiles; triangles are arithmetic means. Means and standard deviation are also reported in Supplemental Information Table 1.")
```

`r f_nums('violin_plots')`
```{r data_summary_gg, fig.cap = violin_cap, fig.height=8, fig.width=6}
LongData <- 
    read_csv(url('https://raw.githubusercontent.com/devanmcg/SpatialFireBehavior/main/data/AnalysisDataKY.csv')) %>% 
    select(-LAI, -JD, -MaxWindSpeed) %>%
    mutate(ros = ifelse(ros >= 10, NA, ros), 
           tHa = ifelse(tHa >=4, NA, tHa)) %>%
    # convert units 
    mutate(WindSpeed = WindSpeed * 0.28,  # km/hr to m/s
           tHa = tHa * 0.1) %>%           # t/ha to kg/m^s
    pivot_longer(cols = AirTemp:tHa, 
                 names_to = 'var', 
                 values_to = 'value') %>%
    mutate(type = case_when(
                    var %in% c('MaxC', 
                               'SoilMaxC', 
                               'ros') ~ 'Fire behavior', 
                    var %in% c('tHa',
                               'FuelMoisture') ~ 'Fuel', 
                    TRUE ~ 'Weather' ), 
           var = recode(var, 
                        AirTemp = 'Air~temperature~(degree*C)', 
                        RH = 'Relative~humidity~(\'%\')', 
                        dpC = 'Dew~point~(degree*C)', 
                        FuelMoisture = 'Total~fuel~moisture~(\'%\')', 
                        tHa = 'Fuel~load~(kg~m^-2)',
                        MaxC = 'Flame~temp~(degree*C)', 
                        WindSpeed = 'Wind~speed~(m~s^-1)', 
                        ros = 'Spread~rate~(m~min^-1)', 
                        SoilMaxC = 'Soil~surface~temp~(degree*C)'), 
           location = recode(location, 
                             H = "Hettinger", 
                             CG = "Central Grasslands"))

>>>>

```{r }
violin_cap <- f_nums(name = "violin_plots", 
                   caption = "Distribution of weather, fuel, and fire behavior data for fires in southwestern North Dakota (Hettinger, dark maroon) and central North Dakota (Central Grasslands, light blue). Horizontal gray lines denote 25%, 50% (median) and 75% quantiles; triangles are arithmetic means. Means and standard deviation are also reported in Supplemental Information Table 1. VPD = Vapor pressure deficit.")
```

`r f_nums('violin_plots')`
```{r data_summary_gg, fig.cap = violin_cap, fig.height=8.25, fig.width=6}
LongData <- 
    read_csv(url('https://raw.githubusercontent.com/devanmcg/SpatialFireBehavior/main/data/AnalysisDataKY.csv')) %>% 
    select(-LAI, -JD, -MaxWindSpeed) %>%
    mutate(ros = ifelse(ros >= 10, NA, ros), 
           tHa = ifelse(tHa >=4, NA, tHa)) %>%
    # convert units 
    mutate(WindSpeed = WindSpeed * 0.28,  # km/hr to m/s
           tHa = tHa * 0.1) %>%           # t/ha to kg/m^s
    pivot_longer(cols = AirTemp:tHa, 
                 names_to = 'var', 
                 values_to = 'value') %>%
    mutate(type = case_when(
                    var %in% c('MaxC', 
                               'SoilMaxC', 
                               'ros') ~ 'Fire behavior', 
                    var %in% c('tHa',
                               'FuelMoisture') ~ 'Fuel', 
                    TRUE ~ 'Weather' ), 
           var = recode(var, 
                        AirTemp = 'Air~temperature~(degree*C)', 
                        RH = 'Relative~humidity~(\'%\')', 
                        dpC = 'Dew~point~(degree*C)', 
                        FuelMoisture = 'Total~fuel~moisture~(\'%\')', 
                        tHa = 'Fuel~load~(kg~m^-2)',
                        MaxC = 'Flame~temp~(degree*C)', 
                        WindSpeed = 'Wind~speed~(m~s^-1)', 
                        ros = 'Spread~rate~(m~min^-1)', 
                        SoilMaxC = 'Soil~surface~temp~(degree*C)'), 
           location = recode(location, 
                             H = "Hettinger", 
                             CG = "Central Grasslands"))
